Describing the scale and composition of calls for service in Detroit

### 2021-09-01 paper.Rmd
writing and maps

Individual incident location coordinates were aggregated to synthetic grid cells laid over the city to generate heatmaps of counts throughout the year. ^[Grid cells were defined as 1000$^2$, a size deemed appropriate based on a balance between capturing localised variation and interpretable visualisations. 2% of incidents were excluded from the spatial visualisations due to incomplete geographic information.]These are visualised for each demand classification in Figure 3.

>>>>

Individual incident location coordinates were aggregated to synthetic grid cells laid over the city to generate heatmaps of counts throughout the year. ^[Grid cells were defined as 1000 ft$^2$ (305m$^2$) -- a size deemed appropriate based on a balance between capturing localised variation and interpretable visualisations. 2% of incidents were excluded from the spatial visualisations due to incomplete geographic information.] These are visualised for each demand classification in Figure 3.

- Community: Wayne State University buildings.
- Crime: Henry Ford Hospital, including the emergency department.
         The hotspot in the far east is also a hosptial, as is the north west one.
- Proactive: Wayne State University buildings, Midtown neighbourhood, just outside
  downtown.
- Quality of life: university disticts, downtown detroit and financial district.
- Health: downtown, universities, schools and detroit rescue mission ministries
